### 2020-03-13 random/career_preparation/cover_letters/nielsen.tex
update

Dear Dropbox,

I am interested in being a Software Engineer Intern for Summer 2020.

@@

I have built a Go-lang based data-scraper for sports odds that initially took 20+ minutes in python, now takes 30 seconds and writes to a MySQL DB on Google Cloud.

I am interested in how larger scale data operations work and how to make scalable software and possibly use machine learning for load balancing.

@@

Anand Jain\\
Computer Science\\
University of Chicago\\

anandj@uchicago.edu\\
Github, Linkedin: anandijain\\
\today\\

>>>>

Dear Nielsen,

I am interested in being a Data Science Internship for Summer 2020.

@@

I have built a Go-lang based data-scraper for sports odds that initially took 20+ minutes in python, now takes 30 seconds.

I am interested in how larger scale data operations work and how to find interesting correlations and abstractions in constrained and big-data scenarios.

@@

Anand Jain\\
anandj@uchicago.edu\\
Github, Linkedin: anandijain\\
\today\\

### 2020-03-13 random/career_preparation/cover_letters/skydio.tex
update

\begin{letter}{Ambarella \\ 3101 Jay Street \\ Santa Clara, CA 95054}

\opening{\textbf{Dear Ambarella,}}

I am interested in being a Software Engineer Intern for Summer 2020.

I believe I have the qualifications in convolutional neural networks, Python, and Go-lang (C++ like) to make a helpful contribution towards creating innovative applications of computer vision. Much of my time in college has been devoted towards thinking about neural network architectures and paradigms, differentiable programming and reinforcement learning being two primary interests. I am looking to further my understanding of the stack by working on embedded machine learning.

>>>>

\begin{letter}{Skydio \\ 114 Hazel Ave \\ Redwood City, CA 94061}

\opening{\textbf{Dear Skydio,}}

I am interested in being an Autonomy Intern for Summer 2020.

I believe I have the qualifications in machine learning, Python, and Go-lang (C++ like) to make a helpful contribution towards creating innovative applications of drone technology. Much of my time in college has been devoted towards thinking about neural network architectures and paradigms, differentiable programming and reinforcement learning being two primary interests. I am looking to further my understanding of the stack by working on embedded machine learning.

### 2020-03-13 random/career_preparation/cover_letters/template2.tex
update

\begin{letter}{Skydio \\ 114 Hazel Ave \\ Redwood City, CA 94061}

\opening{\textbf{Dear Skydio,}}

I am interested in being an Autonomy Intern for Summer 2020.

I believe I have the qualifications in machine learning, Python, and Go-lang (C++ like) to make a helpful contribution towards creating innovative applications of drone technology. Much of my time in college has been devoted towards thinking about neural network architectures and paradigms, differentiable programming and reinforcement learning being two primary interests. I am looking to further my understanding of the stack by working on embedded machine learning.

I have taken an electronics course, where we built radios, stopwatches, and other things in VDHL, as well as an interactive devices course that taught 3D printing and wearable device building. My ideal conversation with an employee would be about autonomy in a multi-agent domain, specifically how to solve the following problem: At UChicago, we have a problem in the winter, many sidewalks need to be cleared and salted on short notice. The current solution is tractors and manually dispersing the salt. I would like to see drones be able to quickly provide a map of unwalkable locations and report this to people cleaning up snow.

>>>>

\begin{letter}{Company \\ Company Address \\ City, State 12345}

\opening{\textbf{Dear Sir or Madam,}}
